Synthesis report

### 2020-05-01 analysis/reports/fia_v_portal.Rmd
make all di

>>>>

# Remove fia sized from all

```{r remove fia sized}

ggplot(filter(all_di, !singletons, s0 > fia_max_s, n0 > fia_max_n), aes(x = skew_percentile)) +
  geom_histogram() +
  theme_bw()

ggplot(filter(all_di, !singletons, s0 > fia_max_s, n0 > fia_max_n), aes(x = skew_percentile)) +
  geom_histogram() +
  theme_bw() +
  facet_wrap(vars(dat), scales = "free_y")

ggplot(filter(all_di, !singletons, s0 > fia_max_s, n0 > fia_max_n), aes(x = simpson_percentile)) +
  geom_histogram() +
  theme_bw()

ggplot(filter(all_di, !singletons, s0 > fia_max_s, n0 > fia_max_n), aes(x = simpson_percentile)) +
  geom_histogram() +
  theme_bw() +
  facet_wrap(vars(dat), scales = "free_y")
```
